% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{NICHOLAS J. GRASEVSKI\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{18 Eglington St \\  Lidcombe, NSW 2141
         \\  grasevski@gmail.com
         \\  0405 634 067
	 \\  github.com/grasevski}
                                  
\begin{resume}

\section{JOB OBJECTIVE}          
    I aspire to spend the rest of my career writing code and honing my craft. Technologies come and go, but I hope to master the underlying fundamentals of programming i.e. physics (hardware constraints), logic (algorithms, type theory) and statistics (scientific computing, machine learning, linear algebra, calculus, etc). I enjoy learning from experienced developers who can show me the path to this goal.
 
\section{EDUCATION}          
    2020-2022: Master of Data Science at USYD (part time, current WAM 86) \\
    2009-2013: Bachelor of Software Engineering with First Class Honors at UNSW (Overall WAM 79.508) \\
    2011: UNSW Computer Science Co-op scholarship \\
    2008: HSC at Caringbah Selective High School (91.6 UAI)

 
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Developer - Javascript, Rust} \>Okta \>Aug 2021 - Present\\
                                       \>Sydney, NSW
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Working in a team contributing to the development of a graphical programming language
    designed to allow our customers to integrate their various systems with Okta's Single
    Sign On identity application. Our team is implementing the full text search functionality
    for the Integrated Development Environment for said programming language, for ease of
    debugging. Personal contributions so far include provisioning the cloud infrastructure
    for the search engine, fixing concurrency bugs and performance bugs in the existing
    system, and implementing the plumbing code to read the logs from the interpreter for the
    programming language and store them in the search engine.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf ML Engineer - Python, Go} \>Rokt \>Mar 2019 - Jun 2021\\
                                   \>Sydney, NSW
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Lead developer for the realtime inference and optimization backend for advertising
    recommendations. This allowed the ML team to quickly experiment with new algorithms and
    deploy them autonomously, such as migrating the models from logistic regression to LightGBM,
    changing the auction mechanics from a greedy algorithm to stochastic hill climbing algorithm
    (which I designed and implemented), implementing a thompson sampling technique for LightGBM
    which I invented, and various other incremental improvements, summing to about 5\% (or
    US\$5M) additional revenue per year. Also did some work on click prediction with LightGBM,
    developing new models and adding new features to existing ones. Last but not least, developed
    and maintained a feature store for recording the click data, which sped up redshift model
    training queries by 20x and reduced SQL lines of code by 3x.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Developer - C++} \>Integrated Research \>Aug 2017 - Feb 2019\\
                                   \>Sydney, NSW
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Improvements and rearchitecting of VOIP monitoring software, with a focus on performance and
    secondary task of improving and augmenting the existing functionality. This involved radical
    architectural changes to improve the performance 100 fold, whilst under tight deadlines and
    also maintaining and improving all existing functionality. Technologies used include C++,
    Javascript, C, windows batch scripts and some Golang.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Developer - PHP} \>Freelancer.com \>Apr 2015 - Aug 2017\\
                                   \>Sydney, NSW
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Maintained and added features to the core payment systems in a legacy
    PHP code base, as well as a Python credit card handling system. Tasks
    include adding new payment methods, improving fraud detection, bug fixing,
    processing credit card data and making changes to core transaction
    processing such as fee handling and delaying transactions. This entailed
    writing cron jobs, SQL queries, and editing PHP business logic, then
    writing tests (unit, integration, end to end, manual) and making little
    refactors along the way to make it a little less error prone to deal with
    next time.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Developer - C++} \>Optiver \>Mar 2014 - Apr 2015\\
                                   \>Sydney, NSW
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Worked in the Hong Kong Futures Exchange team, writing exchange connectivity
    code and autotrader code. Wrote a "market link" microservice to connect to
    the exchange using a combination of its own SDK plus an in-house reverse
    engineered nonblocking version of it, and then translate the exchange
    specific protocol to Optiver's internal generic protocol and expose an
    endpoint for this using Optiver's internal implementation of user space
    pipes (shared memory ring buffers) as well as UDP and TCP. Also worked on an
    exchange simulator, backtester and made a "panic button" service to delete
    all orders in case of emergency. Finally, worked on the arbitrage logic for
    one of the autotrader applications, tweaking the paramaters and logic
    according to human traders' requirements.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Programmer - Haskell, C, C++} \>UNSW \>Sep 2013 - Mar 2014\\
                                       \>Kensington, NSW
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Bug fixes, improvements and additional features to a C++ GUI written using
    the QT library (I wrote negative 2000 LOC on this project). The GUI in
    question was a frontend to a model checker (formal verification) program
    like SPIN and as such I also came up with a design proposal to migrate it
    to a TCL/Tk graphical interface, like SPIN has. The rest of my time was
    spent bug fixing and adding features to the backing Haskell command line
    model checker application and adding tests to it. I also integrated the
    PicoSAT C library as the backing constraint solver for the model checking
    algorithm.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Research Assistant - Java, Perl} \>Smart Services CRC \>Dec 2012 - Mar 2013\\
                                          \>Kensington, NSW
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Data mining tasks for RSVP dating website's recommender system based on
    decision trees. This involved writing command line java applications and
    bash/perl scripts to tokenize text data about consumers' hobbies from an
    Oracle database and put it in a format amenable to machine learning
    algorithms.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Tutor - MS Excel, VBA} \>UNSW     \>2012-2014\\
                                \>Kensington, NSW
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Teaching and demonstrating first year programming to engineering students,
    with a particular focus on MS Excel and VBA macro programming. Duties
    included lab setup and marking.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Programmer - Delphi} \>Mountaintop Systems \> Jan 2011 - Jul 2011\\
                              \>Sutherland, NSW
   \end{tabbing}\vspace{-20pt}
    Bug fixing and minor feature additions to cash register software written
    in Delphi. Also improved the test automation and build system.


\section{COMPUTER SKILLS}          
    Polyglot programmer: AVR assembler, C, C++, Rust, Golang, Haskell, Python, Clojure and so on \\
    System administration: Bash, Kubernetes, AWS, Google Cloud \\
    Network programming: UDP, TCP, packed structs, protobuf, REST \\
    Concurrency and parallelism: SSE, AVX, threads, shared memory, ring buffers, mutexes \\
    Scientific computing: BLAS, Gnu Scientific Library, torch, numpy, tensorflow, ROS \\
    Statistics: regression, kalman filter, Q learning, PID control, gradient boosted decision trees, neural networks
 
 
\section{HONORS AND AWARDS}          
    2021: Top 10 of class (out of a few hundred) for machine learning accuracy, as well as for training and inference speed in COMP5318 assignment \\
    2020: Rokt hackathon Runner Up \\
    2019: Coursera Machine Learning course \\
    2019: Scored 96\% on AWS Associate Architect exam \\
    2019: Professional Scrum Master Level 1 \\
    2018: Rokt "Golden Coder" award \\
    2017: Toastmasters Competent Communicator \\
    2014: Runner up in Spectrum Super Smash Brothers Nintendo 64 competition \\
    2013: Graduated with first class honors \\
    2013: Optiver SENG3011 Prize \\
    2009-2013: UNSW Engineering Dean's Honors List \\
    2008: Distinguished Achievers List in 3 Unit Maths, 3 Unit Music \\
    2008: 1st place in national Generations in Jazz competition with the NSW Arts Unit Jazz Orchestra \\
    2007: Distinguished Achievers List in accelerated HSC Software Design and Development (90/100)
 
\section{EXTRACURRICULAR ACTIVITIES}          
    Football for Lidcombe Congs \\
    Guitar \\
    2015-2017: Toastmasters \\
    2008-2015: UNSW Orchestra, North Sydney Symphony Orchestra, TOPS Orchestra (section leader), various uni revues (band leader) \\
    2005-2008: Schools Spectacular Stage Band/Orchestra
 
\end{resume}
\end{document}
